Crossing Origins by Crossing Formats

### 2012-12-03 main.tex
related work
Almost there.

Coercing content to be interpreted
as a different type can be accommodated in the context of the web. 
If the content is loaded using an \emph{image} tag it will be interpreted 
as an image, if a \emph{script} tag is used it will be interpreted as a script. Some 
tags even let the developer decide which type to interpret the content as. 
To prevent abuse, the browsers employ content-type 
sniffing for certain content-types, a practice which has historically led to 
security issues.
\todo{explain the issues and cite Barth et al.~\cite{Barth+:SP09}}

% Malicious polyglots in literature; gifar, chameleon, cross-origin css attacks
\todo{
In literature we find Content repurposing, content smuggling,
chameleon, gifar; say that we have called it content smuggling
ourselves in case someone discovers the blog
}

@@

According to the PDF specification \todo{cite specification} a PDF file is composed of
a header, several objects, a cross-reference section and a trailer. Listing~\ref{lst:sample-pdf} 
shows a sample of how a PDF file is structured and its elements.

@@

@@

Alexa top 100 results

>>>>

Coercing content to be interpreted
as a different type can be accommodated in the context of the web. 
If the content is loaded using an \emph{image} tag it will be interpreted 
as an image, if a \emph{script} tag is used it will be interpreted as a script. Some 
tags even let the developer decide which type to interpret the content as. 
To prevent abuse, the browsers employ content-type 
sniffing for certain content-types, a practice which has historically led to 
security issues.

Barth et al.~\cite{Barth+:SP09} define \emph{chameleon} documents, 
in which a benign file type crossbred with malicious HTML content. The document 
is crafted in such a way that the content-sniffing algorithm used in the browser 
will detect the content type as HTML. The paper proceeds to 
describe how an attacker can create a 
\emph{chameleon} document, that is valid PostScipt, but will be identified as HTML.
This issue allows exploitation when there is a mismatch between a websites 
content validation filter and the browsers content-sniffing algorithm.

In literature we find, apart from chameleons, other names for similar,
related concepts. Brandis~\cite{Brandis:GIFAR} refer \emph{GIFAR} 
attacks, based on one of the early instances of attacks based on 
GIF/JAR polyglots. 
Sundareswaran et al.~\cite{Sundareswaran:Squicciarini:CEAS10,Sundareswaran:Squicciarini:SecureComm10}
discuss GIFAR-related attacks as a form of \emph{content repurposing} attack. 
In this paper the term content smuggling is used as it best represent 
how a polyglot can infiltrate an origin.

@@

According to the PDF specification~\cite{PDF:ISO08} a PDF file is composed of
a header, several objects, a cross-reference section and a trailer. Listing~\ref{lst:sample-pdf} 
shows a sample of how a PDF file is structured and its elements.

@@

\todo{JavaScript/CSS/JSON context}

@@

A study to evaluate the prevalence of these issues was performed, 
covering the Alexa top 100 websites. Because of their dominance 
on the web, these websites are also the most exposed to security threats.
The study covers PDF-based polyglot attacks using syntax injection as the infiltration method.
The study did not cover polyglot attacks based on content smuggling, as 
potential targets generally require authentication before submitting content.

The study was conducted by supplying the websites with small benign samples 
of PDF syntax, containing keywords and tokens, and examining the responses 
for said tokens. The samples were benign strings containing  The conclusion is 
that nine websites out of the hundred apply insufficient content filtering with 
respect to the PDF format, which have the potential of compromising the 
confidentiality and integrity of the website's users.
